Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/fig-motivation.tex
motivation nits

\begin{figure*}
\centering
\begin{tabular}{lllr}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Weak cryptography used even if user selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

\end{tabular}
\caption{Classification of known vulnerabilities in the CVE database
between 2010 and 2014 related to the search term ``ZIP'' and involving
the ZIP file format.}
\label{fig:motivation} 
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{tabular}{lllr}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption & CVE-2013-5660 & Buffer overflow & 11\\
  Parsing inconsistency & CVE-2013-1462 & Multiple virus scanners interpret ZIP files incorrectly & 4\\
  Semantic misunderstanding & CVE-2014-2319 & Weak cryptography used even if user selects AES & 1\\
\midrule
  \multicolumn{3}{l}{\bf Total of all vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

\end{tabular}
\caption{Classification of vulnerabilities in the CVE database
from 2010 to May 2014 containing the term ``ZIP'' and involving
the ZIP file format.}
\label{fig:motivation} 
\end{figure*}

### 2014-09-10 paper/osdi14/motivation.tex
motivation nits

Three recent high profile security vulnerabilities are due to logic
errors in input processing.  In all cases, when the vulnerabilities were
fixed, a similar flaw was exposed immediately afterwards, showing the
need for a different approach to input handling that eliminates those
vulnerabilities by design.

The Evasi0n jailbreak for iOS 6~\cite{evaders6} relies on the XNU kernel and
user-mode code-signing verifier interpreting executable metadata differently, so the code signature
sees different bytes at a virtual address than kernel maps into the process. The next version of iOS
added an explicit check for this particular metadata inconsistency. However, because parsing and
processing of the input data is still mixed, the jailbreakers could set a flag that re-introduced
the inconsistency after the check, but before signatures are verified~\cite{geohot-evasion}, which
allowed iOS 7 to be jailbroken.

@@

To understand the impact of parsing mistakes in real-world software,
we conducted a systematic study of
vulnerabilities related to ZIP file parsing.  
The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protos-c10-archive} found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling. We extend this study by looking at the CVE database.

@@

These input processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218}, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees, such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers using lower-level languages to avoid these bugs
in the first place.

>>>>

Three recent high-profile security vulnerabilities are due to logic
errors in input processing.  In all cases, when the vulnerabilities were
fixed, a similar flaw was exposed immediately afterwards, showing the
need for a different approach to input handling that eliminates those
vulnerabilities by design.

The Evasi0n jailbreak for iOS 6~\cite{evaders6} relies on the XNU kernel and
user-mode code-signing verifier interpreting executable metadata differently, so the code signature
checker sees different bytes at a virtual address than what the kernel maps into the process. The next version of iOS
added an explicit check for this particular metadata inconsistency. However, because parsing and
processing of the input data is still mixed, the jailbreakers could set a flag that re-introduced
the inconsistency after the check, but before signatures are verified~\cite{geohot-evasion}, which
allowed iOS 7 to be jailbroken.

@@

To understand the impact of parsing mistakes in real-world software,
we conducted a systematic study of
vulnerabilities related to ZIP file parsing.  
The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protos-c10-archive} found numerous security vulnerabilities
related to input handling
in most implementations of ZIP and other archive formats.
We extend this study by looking at the CVE database.

@@

These input-processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times,\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: CVE-2013-5660, -0742, -0138, CVE-2012-4987, -1163, -1162, CVE-2011-2265,
    CVE-2010-4535, -1657, -1336, and -1218.} is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees, such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers using lower-level languages to avoid these bugs
in the first place.
